Quasi-Monte Carlo Methods: What, Why, and How?

### 2025-08-05 Older versions/HickernellMCQMC2024_QMCTutorial_rev_1.tex
small changes from Nathan and Aleksei

One idea for constructing confidence intervals without replications is to approximate the decay rate of Fourier coefficients of $f$. Bounds of absolute certainty have be derived for cones of functions with reasonable decay of their Fourier coefficients \cite{HicEtal17a}. As in the qMC-CLT stopping criterion, one may iteratively double $n$ until the bounds are sufficiently tight. \AGSNote{Figure \ref{fig:asian_option_pda_vs_chol} compares these decay-tracking qMC algorithms against IID Monte Carlo stopping criterion across a variety of tolerances for pricing an Asian option from finance \cite[p.\ 8]{Gla03}.}

@@

\begin{figure}
	\centering
 %    \includegraphics[width = 0.48\textwidth]{\figpath//NumSamples_Asian_Option_tol_0.001_d52.pdf}
	% \includegraphics[width = 0.48\textwidth]{\figpath/Times_Asian_Option_tol_0.001_d52.pdf} \quad 
    \includegraphics[width = 1\textwidth]{\figpath//Times_NumSamples_Asian_Option_tol_0.001_d52.pdf}
	\caption{\AGSNote{Comparison of IID Monte Carlo and qMC stopping criteria for estimating the fair price of an Asian option with arithmetic mean. For QMC with Sobol' points, using a principal component analysis (PCA) decomposition of the Brownian motion provides substantial savings compared to the Cholesky decomposition. Using an Asian option with geometric mean control variate (CV) provides additional savings. \label{fig:asian_option_pda_vs_chol}}}
\end{figure}

>>>>

One idea for constructing confidence intervals without replications is to approximate the decay rate of Fourier coefficients of $f$. Bounds of absolute certainty have be derived for cones of functions with reasonable decay of their Fourier coefficients \cite{HicEtal17a}. As in the qMC-CLT stopping criterion, one may iteratively double $n$ until the bounds are sufficiently tight. \AGSNote{Figure \ref{fig:asian_option_pda_vs_chol} compares these decay-tracking qMC algorithms against IID Monte Carlo stopping criterion across a range of tolerances for pricing an Asian option from finance \cite[p.\ 8]{Gla03}.}

@@

\begin{figure}
	\centering
 %    \includegraphics[width = 0.48\textwidth]{\figpath//NumSamples_Asian_Option_tol_0.001_d52.pdf}
	% \includegraphics[width = 0.48\textwidth]{\figpath/Times_Asian_Option_tol_0.001_d52.pdf} \quad 
    \includegraphics[width = 1\textwidth]{\figpath//Times_NumSamples_Asian_Option_tol_0.001_d52.pdf}
	\caption{\AGSNote{Comparison of IID Monte Carlo and qMC stopping criteria for estimating the fair price of an Asian option with arithmetic mean. For qMC with Sobol' points, using a principal component analysis (PCA) decomposition of the Brownian motion provides substantial savings compared to the Cholesky decomposition. Using an Asian option with geometric mean control variate (CV) provides additional savings. \label{fig:asian_option_pda_vs_chol}}}
\end{figure}
